---
title: "SARS-CoV-2 antibody dynamics, within-household transmission and the impact of contact tracing from community-wide serological testing in the Italian municipality of Vo'"
author: "Dorigatti I. et al. (2021)"
date: "12/05/2021"
output:
   rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---


This code outputs complementary info for Figures S1, and Tables S5 and S6.


**Load packages**
```{r, message=FALSE}
library(boot)
library(kableExtra)
library(ppcor)
library(readxl)
```

**Read data**
```{r, warning=FALSE, message=FALSE}
Vo_serology_data = read_excel("data/Vo_serology_data.xlsx", sheet="Dataset")
```


Figure S1
=========

*Association among serological and micro-neutralisation assays*

May serosurvey
--------------

**Extract dataset**
```{r}
May_survey = data.frame(Vo_serology_data[,c(269,271,273,275,302)])
May_survey[May_survey=="NA"] = NA
May_survey[,4] = as.factor(May_survey[,4])
May_survey[,4] = factor(May_survey[,4], levels = levels(May_survey[,4]),
                      labels=paste(c(10, 10, 1280, 160, 20, 320, 40, 640, 80, 0)))
May_survey = May_survey[!apply(May_survey, 1, function(x) any(is.na(x))),]
May_survey = as.data.frame(apply(May_survey, 2, as.numeric))

May_survey[May_survey == 0] = 1

May_survey = log(May_survey, base=10)
colnames(May_survey) = c("Diasorin", "Abbott", "Roche", "Neutralization","Groundtruth")
```

**Pairs plots of serological and micro-neutralisation assays on the decadic log scale**

```{r, fig.cap="Upper panels: marginal Pearson correlation; lower panels: partial Pearson correlations.  In red: correlations significant at the 5% level"}

par(mfrow=c(4,4), pty="s", mar=c(2, 0, 2, 0))
#
with(May_survey,
     { hist(Neutralization, main="Neutralization", xlab="values", ylab="frequency") ;
       rug(Neutralization) })
with(May_survey,
     { plot(Neutralization~Diasorin, cex=0.5) ; abline(lm(Neutralization~Diasorin)) ;
       corr = cor.test(Neutralization, Diasorin)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { plot(Neutralization~Abbott, cex=0.5) ; abline(lm(Neutralization~Abbott)) ;
       corr = cor.test(Neutralization, Abbott)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { plot(Neutralization~Roche, cex=0.5) ; abline(lm(Neutralization~Roche)) ;
       corr = cor.test(Neutralization, Roche)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
#
with(May_survey,
     { N.res = resid(lm(Neutralization~Abbott+Roche)) ;
       D.res = resid(lm(Diasorin~Abbott+Roche)) ;
       plot(N.res~D.res, cex=0.5) ; abline(lm(N.res~D.res)) ;
       corr = pcor.test(Neutralization, Diasorin, cbind(Abbott, Roche))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { hist(Diasorin, main="Diasorin", xlab="values", ylab="frequency") ;
       rug(Diasorin) })
with(May_survey,
     { plot(Diasorin~Abbott, cex=0.5) ; abline(lm(Diasorin~Abbott)) ;
       corr = cor.test(Diasorin, Abbott)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { plot(Diasorin~Roche, cex=0.5) ; abline(lm(Diasorin~Roche)) ;
       corr = cor.test(Diasorin, Roche)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
#
with(May_survey,
     { N.res = resid(lm(Neutralization~Diasorin+Roche)) ;
       A.res = resid(lm(Abbott~Diasorin+Roche)) ;
       plot(N.res~A.res, cex=0.5) ; abline(lm(N.res~A.res)) ;
       corr = pcor.test(Neutralization, Abbott, cbind(Diasorin, Roche))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { D.res = resid(lm(Diasorin~Neutralization+Roche)) ;
       A.res = resid(lm(Abbott~Neutralization+Roche)) ;
       plot(D.res~A.res, cex=0.5) ; abline(lm(D.res~A.res)) ;
       corr = pcor.test(Diasorin, Abbott, cbind(Neutralization, Roche))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { hist(Abbott, main="Abbott", xlab="values", ylab="frequency") ;
       rug(Abbott) })
with(May_survey,
     { plot(Abbott~Roche, cex=0.5) ; abline(lm(Abbott~Roche)) ;
       corr = cor.test(Abbott, Roche)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
#
with(May_survey,
     { N.res = resid(lm(Neutralization~Diasorin+Abbott)) ;
       R.res = resid(lm(Roche~Diasorin+Abbott)) ;
       plot(N.res~R.res, cex=0.5) ; abline(lm(N.res~R.res)) ;
       corr = pcor.test(Neutralization, Roche, cbind(Diasorin, Abbott))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { D.res = resid(lm(Diasorin~Neutralization+Abbott)) ;
       R.res = resid(lm(Roche~Neutralization+Abbott)) ;
       plot(D.res~R.res, cex=0.5) ; abline(lm(D.res~R.res)) ;
       corr = pcor.test(Diasorin, Roche, cbind(Neutralization, Abbott))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { A.res = resid(lm(Abbott~Neutralization+Diasorin)) ;
       R.res = resid(lm(Roche~Neutralization+Diasorin)) ;
       plot(A.res~R.res, cex=0.5) ; abline(lm(A.res~R.res)) ;
       corr = pcor.test(Abbott, Roche, cbind(Neutralization, Diasorin))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(May_survey,
     { hist(Roche, main="Roche", xlab="values", ylab="frequency") ;
       rug(Roche) })
```

**Pearson's correlations**

```{r}
cor.tab = matrix(NA, nrow=4, ncol=4)
diag(cor.tab) = 1
cor.tab[1,2] = with(May_survey, cor.test(Neutralization, Diasorin)$estimate)
cor.tab[1,3] = with(May_survey, cor.test(Neutralization, Abbott)$estimate)
cor.tab[1,4] = with(May_survey, cor.test(Neutralization, Roche)$estimate)
cor.tab[2,1] = with(May_survey, pcor.test(Neutralization, Diasorin, cbind(Abbott, Roche))$estimate)
cor.tab[2,3] = with(May_survey, cor.test(Diasorin, Abbott)$estimate)
cor.tab[2,4] = with(May_survey, cor.test(Diasorin, Roche)$estimate)
cor.tab[3,1] = with(May_survey, pcor.test(Neutralization, Abbott, cbind(Diasorin, Roche))$estimate)
cor.tab[3,2] = with(May_survey, pcor.test(Diasorin, Abbott, cbind(Neutralization, Roche))$estimate)
cor.tab[3,4] = with(May_survey, cor.test(Abbott, Roche)$estimate)
cor.tab[4,1] = with(May_survey, pcor.test(Neutralization, Roche, cbind(Diasorin, Abbott))$estimate)
cor.tab[4,2] = with(May_survey, pcor.test(Diasorin, Roche, cbind(Neutralization, Abbott))$estimate)
cor.tab[4,3] = with(May_survey, pcor.test(Abbott, Roche, cbind(Neutralization, Diasorin))$estimate)
cor.tab = round(cor.tab, 2)
cor.tab = as.data.frame(cor.tab)
dimnames(cor.tab) = list(c("Neutralization", "Diasorin","Abbott","Roche"), c("Neutralization", "Diasorin","Abbott","Roche"))
kbl(cor.tab)
```

**p-values of Pearson's correlations**

```{r}
p.tab = matrix(NA, nrow=4, ncol=4)
p.tab[1,2] = with(May_survey, cor.test(Neutralization, Diasorin)$p.value)
p.tab[1,3] = with(May_survey, cor.test(Neutralization, Abbott)$p.value)
p.tab[1,4] = with(May_survey, cor.test(Neutralization, Roche)$p.value)
p.tab[2,1] = with(May_survey, pcor.test(Neutralization, Diasorin, cbind(Abbott, Roche))$p.value)
p.tab[2,3] = with(May_survey, cor.test(Diasorin, Abbott)$p.value)
p.tab[2,4] = with(May_survey, cor.test(Diasorin, Roche)$p.value)
p.tab[3,1] = with(May_survey, pcor.test(Neutralization, Abbott, cbind(Diasorin, Roche))$p.value)
p.tab[3,2] = with(May_survey, pcor.test(Diasorin, Abbott, cbind(Neutralization, Roche))$p.value)
p.tab[3,4] = with(May_survey, cor.test(Abbott, Roche)$p.value)
p.tab[4,1] = with(May_survey, pcor.test(Neutralization, Roche, cbind(Diasorin, Abbott))$p.value)
p.tab[4,2] = with(May_survey, pcor.test(Diasorin, Roche, cbind(Neutralization, Abbott))$p.value)
p.tab[4,3] = with(May_survey, pcor.test(Abbott, Roche, cbind(Neutralization, Diasorin))$p.value)
p.tab = round(p.tab, 3)
p.tab = as.data.frame(p.tab)
dimnames(p.tab) = list(c("Neutralization", "Diasorin","Abbott","Roche"), c("Neutralization", "Diasorin","Abbott","Roche"))
kbl(p.tab)
```

November serosurvey
-------------------

**Extract dataset**
```{r}
Nov_survey = data.frame(Vo_serology_data[,c(306,308,310,312,302)])
Nov_survey[Nov_survey=="NA"] = NA
Nov_survey[,4] = as.factor(Nov_survey[,4])
Nov_survey[,4] = factor(Nov_survey[,4], levels = levels(Nov_survey[,4]),
                      labels=paste(c(10, 320, 10, 1280, 160, 20, 320, 40, 80, 0)))
Nov_survey = Nov_survey[!apply(Nov_survey, 1, function(x) any(is.na(x))),]
Nov_survey = as.data.frame(apply(Nov_survey, 2, as.numeric))

Nov_survey[Nov_survey == 0] = 1

Nov_survey = log(Nov_survey, base=10)
colnames(Nov_survey) = c("Diasorin", "Abbott", "Roche", "Neutralization")
```

**Pairs plots of serological and micro-neutralisation assays on the decadice log scale**

```{r, fig.cap="Upper panels: marginal Pearson correlation; lower panels: partial Pearson correlations.  In red: correlations significant at the 5% level"}

par(mfrow=c(4,4), pty="s", mar=c(2, 0, 2, 0))
#
with(Nov_survey,
     { hist(Neutralization, main="Neutralization", xlab="values", ylab="frequency") ;
       rug(Neutralization) })
with(Nov_survey,
     { plot(Neutralization~Diasorin, cex=0.5) ; abline(lm(Neutralization~Diasorin)) ;
       corr = cor.test(Neutralization, Diasorin)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { plot(Neutralization~Abbott, cex=0.5) ; abline(lm(Neutralization~Abbott)) ;
       corr = cor.test(Neutralization, Abbott)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { plot(Neutralization~Roche, cex=0.5) ; abline(lm(Neutralization~Roche)) ;
       corr = cor.test(Neutralization, Roche)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
#
with(Nov_survey,
     { N.res = resid(lm(Neutralization~Abbott+Roche)) ;
       D.res = resid(lm(Diasorin~Abbott+Roche)) ;
       plot(N.res~D.res, cex=0.5) ; abline(lm(N.res~D.res)) ;
       corr = pcor.test(Neutralization, Diasorin, cbind(Abbott, Roche))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { hist(Diasorin, main="Diasorin", xlab="values", ylab="frequency") ;
       rug(Diasorin) })
with(Nov_survey,
     { plot(Diasorin~Abbott, cex=0.5) ; abline(lm(Diasorin~Abbott)) ;
       corr = cor.test(Diasorin, Abbott)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { plot(Diasorin~Roche, cex=0.5) ; abline(lm(Diasorin~Roche)) ;
       corr = cor.test(Diasorin, Roche)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
#
with(Nov_survey,
     { N.res = resid(lm(Neutralization~Diasorin+Roche)) ;
       A.res = resid(lm(Abbott~Diasorin+Roche)) ;
       plot(N.res~A.res, cex=0.5) ; abline(lm(N.res~A.res)) ;
       corr = pcor.test(Neutralization, Abbott, cbind(Diasorin, Roche))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { D.res = resid(lm(Diasorin~Neutralization+Roche)) ;
       A.res = resid(lm(Abbott~Neutralization+Roche)) ;
       plot(D.res~A.res, cex=0.5) ; abline(lm(D.res~A.res)) ;
       corr = pcor.test(Diasorin, Abbott, cbind(Neutralization, Roche))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { hist(Abbott, main="Abbott", xlab="values", ylab="frequency") ;
       rug(Abbott) })
with(Nov_survey,
     { plot(Abbott~Roche, cex=0.5) ; abline(lm(Abbott~Roche)) ;
       corr = cor.test(Abbott, Roche)
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
#
with(Nov_survey,
     { N.res = resid(lm(Neutralization~Diasorin+Abbott)) ;
       R.res = resid(lm(Roche~Diasorin+Abbott)) ;
       plot(N.res~R.res, cex=0.5) ; abline(lm(N.res~R.res)) ;
       corr = pcor.test(Neutralization, Roche, cbind(Diasorin, Abbott))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { D.res = resid(lm(Diasorin~Neutralization+Abbott)) ;
       R.res = resid(lm(Roche~Neutralization+Abbott)) ;
       plot(D.res~R.res, cex=0.5) ; abline(lm(D.res~R.res)) ;
       corr = pcor.test(Diasorin, Roche, cbind(Neutralization, Abbott))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { A.res = resid(lm(Abbott~Neutralization+Diasorin)) ;
       R.res = resid(lm(Roche~Neutralization+Diasorin)) ;
       plot(A.res~R.res, cex=0.5) ; abline(lm(A.res~R.res)) ;
       corr = pcor.test(Abbott, Roche, cbind(Neutralization, Diasorin))
       title(paste(round(corr$est, 2)), cex.main=2, col.main=ifelse(corr$p.v >=0.01, "black", "red"))
       })
with(Nov_survey,
     { hist(Roche, main="Roche", xlab="values", ylab="frequency") ;
       rug(Roche) })
```

**Pearson's correlations**
```{r}
cor.tab = matrix(NA, nrow=4, ncol=4)
diag(cor.tab) = 1
cor.tab[1,2] = with(Nov_survey, cor.test(Neutralization, Diasorin)$estimate)
cor.tab[1,3] = with(Nov_survey, cor.test(Neutralization, Abbott)$estimate)
cor.tab[1,4] = with(Nov_survey, cor.test(Neutralization, Roche)$estimate)
cor.tab[2,1] = with(Nov_survey, pcor.test(Neutralization, Diasorin, cbind(Abbott, Roche))$estimate)
cor.tab[2,3] = with(Nov_survey, cor.test(Diasorin, Abbott)$estimate)
cor.tab[2,4] = with(Nov_survey, cor.test(Diasorin, Roche)$estimate)
cor.tab[3,1] = with(Nov_survey, pcor.test(Neutralization, Abbott, cbind(Diasorin, Roche))$estimate)
cor.tab[3,2] = with(Nov_survey, pcor.test(Diasorin, Abbott, cbind(Neutralization, Roche))$estimate)
cor.tab[3,4] = with(Nov_survey, cor.test(Abbott, Roche)$estimate)
cor.tab[4,1] = with(Nov_survey, pcor.test(Neutralization, Roche, cbind(Diasorin, Abbott))$estimate)
cor.tab[4,2] = with(Nov_survey, pcor.test(Diasorin, Roche, cbind(Neutralization, Abbott))$estimate)
cor.tab[4,3] = with(Nov_survey, pcor.test(Abbott, Roche, cbind(Neutralization, Diasorin))$estimate)
cor.tab = round(cor.tab, 2)
cor.tab = as.data.frame(cor.tab)
dimnames(cor.tab) = list(c("Neutralization", "Diasorin","Abbott","Roche"), c("Neutralization", "Diasorin","Abbott","Roche"))
kbl(cor.tab)
```

**p-values of Pearson's correlations**
```{r}
p.tab = matrix(NA, nrow=4, ncol=4)
p.tab[1,2] = with(Nov_survey, cor.test(Neutralization, Diasorin)$p.value)
p.tab[1,3] = with(Nov_survey, cor.test(Neutralization, Abbott)$p.value)
p.tab[1,4] = with(Nov_survey, cor.test(Neutralization, Roche)$p.value)
p.tab[2,1] = with(Nov_survey, pcor.test(Neutralization, Diasorin, cbind(Abbott, Roche))$p.value)
p.tab[2,3] = with(Nov_survey, cor.test(Diasorin, Abbott)$p.value)
p.tab[2,4] = with(Nov_survey, cor.test(Diasorin, Roche)$p.value)
p.tab[3,1] = with(Nov_survey, pcor.test(Neutralization, Abbott, cbind(Diasorin, Roche))$p.value)
p.tab[3,2] = with(Nov_survey, pcor.test(Diasorin, Abbott, cbind(Neutralization, Roche))$p.value)
p.tab[3,4] = with(Nov_survey, cor.test(Abbott, Roche)$p.value)
p.tab[4,1] = with(Nov_survey, pcor.test(Neutralization, Roche, cbind(Diasorin, Abbott))$p.value)
p.tab[4,2] = with(Nov_survey, pcor.test(Diasorin, Roche, cbind(Neutralization, Abbott))$p.value)
p.tab[4,3] = with(Nov_survey, pcor.test(Abbott, Roche, cbind(Neutralization, Diasorin))$p.value)
p.tab = round(p.tab, 3)
p.tab = as.data.frame(p.tab)
dimnames(p.tab) = list(c("Neutralization", "Diasorin","Abbott","Roche"), c("Neutralization", "Diasorin","Abbott","Roche"))
kbl(p.tab)
```


Table S5
========

*Frequency of comorbidities in symptomatic and asymptomatic SARS-CoV-2 infected individuals*

**Extract datasets**
```{r}
which_symptomatic = 12
which_comorbidity = 280:287
which_groundtruth = 302:304

comorbidities = Vo_serology_data[,c(which_symptomatic, which_comorbidity, which_groundtruth)]
```

Groundtruth
-----------
```{r, warning=FALSE}
comorb_gt = comorbidities[!is.na(comorbidities[,10]),]
dim(comorb_gt)

tmp = comorb_gt[,1]
tmp[!is.na(tmp)] = "symptomatic"
tmp[is.na(tmp)] = "asymptomatic"
comorb_gt[,1] = tmp
#
tmp = as.matrix(comorb_gt[,c(2:9)])
tmp[is.na(tmp)] = "absent"
tmp[tmp == "1"] = "present"
comorb_gt[,c(2:9)] = tmp
```

```{r, warning=FALSE}
for(idx in c(2:6, 8:9))
{
print(table(comorb_gt[,c(idx,1)]))
print(fisher.test(table(comorb_gt[,c(idx,1)])))
}
```

Groundtruth direct contacts
---------------------------
```{r, warning=FALSE}
comorb_gtdc = comorbidities[!is.na(comorbidities[,11]),]
dim(comorb_gtdc)

tmp = comorb_gtdc[,1]
tmp[!is.na(tmp)] = "symptomatic"
tmp[is.na(tmp)] = "asymptomatic"
comorb_gtdc[,1] = tmp
#
tmp = as.matrix(comorb_gtdc[,c(2:9)])
tmp[is.na(tmp)] = "absent"
tmp[tmp == "1"] = "present"
comorb_gtdc[,c(2:9)] = tmp
```

```{r}
for(idx in c(2:6, 8:9))
{
print(table(comorb_gtdc[,c(idx,1)]))
print(fisher.test(table(comorb_gtdc[,c(idx,1)])))
}
```

Groundtruth indirect contacts
-----------------------------
```{r}
comorb_gtic = comorbidities[!is.na(comorbidities[,12]),]
dim(comorb_gtic)

tmp = comorb_gtic[,1]
tmp[!is.na(tmp)] = "symptomatic"
tmp[is.na(tmp)] = "asymptomatic"
comorb_gtic[,1] = tmp
#
tmp = as.matrix(comorb_gtic[,c(2:9)])
tmp[is.na(tmp)] = "absent"
tmp[tmp == "1"] = "present"
comorb_gtic[,c(2:9)] = tmp
```

```{r}
for(idx in c(2:6, 8:9))
{
print(table(comorb_gtic[,c(idx,1)]))
print(fisher.test(table(comorb_gtic[,c(idx,1)])))
}
```


Table S6
========

*Frequency of medication type in symptomatic and asymptomatic SARS-Cov-2 infected individuals*

**Extract datasets**
```{r}
which_symptomatic = 12
which_medication = 288:301
which_groundtruth = 302:304

medications = Vo_serology_data[,c(which_symptomatic, which_medication, which_groundtruth)]
```

Groundtruth
-----------
```{r, warning=FALSE}
medic_gt = medications[!is.na(medications[,16]),]
dim(medic_gt)

tmp = medic_gt[,1]
tmp[!is.na(tmp)] = "symptomatic"
tmp[is.na(tmp)] = "asymptomatic"
medic_gt[,1] = tmp
#
tmp = as.matrix(medic_gt[,c(2:15)])
tmp[is.na(tmp)] = "absent"
tmp[tmp == "1"] = "present"
tmp[tmp == " 1"] = "present"
medic_gt[,c(2:15)] = tmp
```

```{r}
for(idx in c(2:15))
{
print(table(medic_gt[,c(idx,1)]))
print(fisher.test(table(medic_gt[,c(idx,1)])))
}
```

Groundtruth direct contacts
---------------------------
```{r, warning=FALSE}
medic_gtdc = medications[!is.na(medications[,17]),]
dim(medic_gtdc)

tmp = medic_gtdc[,1]
tmp[!is.na(tmp)] = "symptomatic"
tmp[is.na(tmp)] = "asymptomatic"
medic_gtdc[,1] = tmp
#
tmp = as.matrix(medic_gtdc[,c(2:15)])
tmp[is.na(tmp)] = "absent"
tmp[tmp == "1"] = "present"
medic_gtdc[,c(2:15)] = tmp
```

```{r}
for(idx in c(2:15))
{
print(table(medic_gtdc[,c(idx,1)]))
print(fisher.test(table(medic_gtdc[,c(idx,1)])))
}
```

Groundtruth indirect contacts
-----------------------------
```{r, warning=FALSE}
medic_gtic = medications[!is.na(medications[,18]),]
dim(medic_gtic)

tmp = medic_gtic[,1]
tmp[!is.na(tmp)] = "symptomatic"
tmp[is.na(tmp)] = "asymptomatic"
medic_gtic[,1] = tmp
#
tmp = as.matrix(medic_gtic[,c(2:15)])
tmp[is.na(tmp)] = "absent"
tmp[tmp == "1"] = "present"
medic_gtic[,c(2:15)] = tmp
```

```{r}
for(idx in c(2:15))
{
print(table(medic_gtic[,c(idx,1)]))
print(fisher.test(table(medic_gtic[,c(idx,1)])))
}
```
